---
title: "SummaryPlot"
author: "Xiang Ji"
date: "December 29, 2014"
output: word_document
---

This R script is used for generating summary plot for the Geneconv project

1, Read in tables
```{r}
rm(list=ls())  # clean up workspace
path <- "/Users/xji3/Genconv/NewClusterPackRun/NewPackageNewRun/OldResults01152015/"
#path <- "G:/Geneconv/NewClusterPackRun/NewPackageNewRun/"
#HKY_clock_summary <- "HKY_clock_summary"
summary.list <- c( "HKY_nonclock_summary",
                  "HKY_clock_summary",
                  "MG94_clock_summary",
                  "MG94_nonclock_summary", 
                  "Force_HKY_clock_summary", 
                  "Force_HKY_nonclock_summary",
                  "Force_MG94_clock_summary", 
                  "Force_MG94_nonclock_summary"
                  )
#summary.list <- c("Force_MG94_clock_summary")
for (target.summary in summary.list){
  summary_file <- paste(path, target.summary, '.txt', sep = '')
  all <- readLines(summary_file, n = -1)
  col.names <- strsplit(all[1], ' ')[[1]][-1]
  row.names <- strsplit(all[length(all)], ' ')[[1]][-1]
  summary_mat <- as.matrix(read.table(summary_file, 
                                        row.names = row.names, 
                                        col.names = col.names))
  assign(target.summary, summary_mat)
  
  para.list <- c(2:20)
  for (i in para.list){
    image.name <- paste(path, 'Rscripts/', target.summary, '_',
                        row.names[i], '.png', sep = '')
    png(image.name)
    plot(summary_mat[1, ], summary_mat[i, ],
         xlab = row.names[1], ylab = row.names[i],
         main = target.summary)
    dev.off()
    }
  
  
}


```

Now generate summary file of only pairs that have all cases finished in HKY or MG94 models.

```{r}
# HKY
HKY.pair.names <- intersect(intersect(intersect(colnames(HKY_clock_summary), 
                            colnames(HKY_nonclock_summary)),
                            colnames(Force_HKY_clock_summary)),
                            colnames(Force_HKY_nonclock_summary))
HKY.clock.filtered <- HKY_clock_summary[, HKY.pair.names]
HKY.nonclock.filtered <- HKY_nonclock_summary[, HKY.pair.names]
HKY.Force.clock.filtered <- Force_HKY_clock_summary[, HKY.pair.names]
HKY.Force.nonclock.filtered <- Force_HKY_nonclock_summary[, HKY.pair.names]

write.table(HKY.clock.filtered, paste( path, "HKY_clock_filtered", sep = ""))
write.table(HKY.nonclock.filtered, paste( path, "HKY_nonclock_filtered", sep = ""))
write.table(HKY.Force.clock.filtered, paste( path, "HKY_Force_clock_filtered", sep = ""))
write.table(HKY.Force.nonclock.filtered, paste( path, "HKY_Force_nonclock_filtered", sep = ""))



# MG94
MG94.pair.names <- intersect(intersect(intersect(colnames(MG94_clock_summary), 
                            colnames(MG94_nonclock_summary)),
                            colnames(Force_MG94_clock_summary)),
                            colnames(Force_MG94_nonclock_summary))
MG94.clock.filtered <- MG94_clock_summary[, MG94.pair.names]
MG94.nonclock.filtered <- MG94_nonclock_summary[, MG94.pair.names]
MG94.Force.clock.filtered <- Force_MG94_clock_summary[, MG94.pair.names]
MG94.Force.nonclock.filtered <- Force_MG94_nonclock_summary[, MG94.pair.names]

write.table(MG94.clock.filtered, paste( path, "MG94_clock_filtered", sep = ""))
write.table(MG94.nonclock.filtered, paste( path, "MG94_nonclock_filtered", sep = ""))
write.table(MG94.Force.clock.filtered, paste( path, "MG94_Force_clock_filtered", sep = ""))
write.table(MG94.Force.nonclock.filtered, paste( path, "MG94_Force_nonclock_filtered", sep = ""))
```


Now analyze the results

First, show the loglikelihood improvement for each model with/without tau

```{r}
# HKY nonclock
(HKY.nonclock.filtered - HKY.Force.nonclock.filtered)[2,]
# HKY clock
(HKY.clock.filtered - HKY.Force.clock.filtered)[2,]
# MG94 nonclock
(MG94.nonclock.filtered - MG94.Force.nonclock.filtered)[2,]
# MG94 clock
(MG94.clock.filtered - MG94.Force.clock.filtered)[2,]
```

Now plot Total blen v.s. Tau into different groups (differ by color)

HKY nonclock case
```{r}
plot(colSums(HKY.nonclock.filtered[9:20, ]), HKY.nonclock.filtered[8, ],
     type = "n", xlab = "Total branch length", ylab = "Tau" )
col.color <- rep("black", dim(HKY.nonclock.filtered)[2])
col.color[(HKY.nonclock.filtered - HKY.Force.nonclock.filtered)[2,] < 50] <- "red"
points(x = colSums(HKY.nonclock.filtered[9:20, ]), y = HKY.nonclock.filtered[8, ],
       type = "p", col = col.color, bg = col.color)
legend("topright", c("lnL improvement > 50", "lnL improvement < 50"),
       lty = c(1, 1), 
       lwd = c(2.5, 2.5),
       col = c("black", "red"))
title("HKY nonclock")
```

HKY clock case
```{r}
plot(colSums(HKY.clock.filtered[9:20, ]), HKY.clock.filtered[8, ],
     type = "n", xlab = "Total branch length", ylab = "Tau" )
col.color <- rep("black", dim(HKY.clock.filtered)[2])
col.color[(HKY.clock.filtered - HKY.Force.clock.filtered)[2,] < 50] <- "red"
points(x = colSums(HKY.clock.filtered[9:20, ]), y = HKY.clock.filtered[8, ],
       type = "p", col = col.color, bg = col.color)
legend("topright", c("lnL improvement > 50", "lnL improvement < 50"),
       lty = c(1, 1), 
       lwd = c(2.5, 2.5),
       col = c("black", "red"))
title("HKY clock")
```

MG94 nonclock case
```{r}
improvement.lmt <- 20
plot(colSums(MG94.nonclock.filtered[9:20, ]), MG94.nonclock.filtered[8, ],
     type = "n", xlab = "Total branch length", ylab = "Tau" )
col.color <- rep("black", dim(MG94.nonclock.filtered)[2])
col.color[(MG94.nonclock.filtered - MG94.Force.nonclock.filtered)[2,] < improvement.lmt] <- "red"
points(x = colSums(MG94.nonclock.filtered[9:20, ]), y = MG94.nonclock.filtered[8, ],
       type = "p", col = col.color, bg = col.color)
legend("topright", 
       c(paste("lnL improvement > ", toString(improvement.lmt), sep = ""),
         paste("lnL improvement < ", toString(improvement.lmt), sep = "")),
       lty = c(1, 1), 
       lwd = c(2.5, 2.5),
       col = c("black", "red"))
title("MG94 nonclock")
```

MG94 clock case
```{r}
improvement.lmt <- 20
plot(colSums(MG94.clock.filtered[9:20, ]), MG94.clock.filtered[8, ],
     type = "n", xlab = "Total branch length", ylab = "Tau" )
col.color <- rep("black", dim(MG94.clock.filtered)[2])
col.color[(MG94.clock.filtered - MG94.Force.clock.filtered)[2,] < improvement.lmt] <- "red"
points(x = colSums(MG94.clock.filtered[9:20, ]), y = MG94.clock.filtered[8, ],
       type = "p", col = col.color, bg = col.color)
legend("topright", 
       c(paste("lnL improvement > ", toString(improvement.lmt), sep = ""),
         paste("lnL improvement < ", toString(improvement.lmt), sep = "")),
       lty = c(1, 1), 
       lwd = c(2.5, 2.5),
       col = c("black", "red"))
title("MG94 clock")
```

Now see if the pairs red in HKY are also red in MG94

nonclock case
```{r}
HKY.pair.names[(HKY.nonclock.filtered - HKY.Force.nonclock.filtered)[2,] < 50]
MG94.pair.names[(MG94.nonclock.filtered - MG94.Force.nonclock.filtered)[2,] < improvement.lmt]
```

Only 3 pairs show up in both: YLR406C_YDL075W, YIL057C_YER067W, YDR438W_YML018C.


clock case
```{r}
HKY.pair.names[(HKY.clock.filtered - HKY.Force.clock.filtered)[2,] < 50]
MG94.pair.names[(MG94.clock.filtered - MG94.Force.clock.filtered)[2,] < improvement.lmt]
```

2 pairs show up in both: YLR406C_YDL075W, YDR438W_YML018C

=========================================


Now plot Total blen v.s. Tau into different groups (differ by lnL improvement per site)

HKY nonclock case
```{r}
plot(colSums(HKY.nonclock.filtered[9:20, ]), HKY.nonclock.filtered[8, ],
     type = "n", xlab = "Total branch length", ylab = "Tau" )
col.color <- rep("black", dim(HKY.nonclock.filtered)[2])
col.color[((HKY.nonclock.filtered - HKY.Force.nonclock.filtered)[2,] /  HKY.nonclock.filtered[1, ]) < 0.06] <- "red"
points(x = colSums(HKY.nonclock.filtered[9:20, ]), y = HKY.nonclock.filtered[8, ],
       type = "p", col = col.color, bg = col.color)
legend("topright", c("lnL improvement per site > 0.06",
                     "lnL improvement per site < 0.06"),
       lty = c(1, 1), 
       lwd = c(2.5, 2.5),
       col = c("black", "red"))
title("HKY nonclock")

# lnL improvement per site
((HKY.nonclock.filtered - HKY.Force.nonclock.filtered)[2,] /  HKY.nonclock.filtered[1, ])
```

HKY clock case
```{r}
plot(colSums(HKY.clock.filtered[9:20, ]), HKY.clock.filtered[8, ],
     type = "n", xlab = "Total branch length", ylab = "Tau" )
col.color <- rep("black", dim(HKY.clock.filtered)[2])
col.color[((HKY.clock.filtered - HKY.Force.clock.filtered)[2,] /  HKY.clock.filtered[1, ]) < 0.06] <- "red"
points(x = colSums(HKY.clock.filtered[9:20, ]), y = HKY.clock.filtered[8, ],
       type = "p", col = col.color, bg = col.color)
legend("topright", c("lnL improvement per site > 0.06",
                     "lnL improvement per site < 0.06"),
       lty = c(1, 1), 
       lwd = c(2.5, 2.5),
       col = c("black", "red"))
title("HKY clock")

# lnL improvement per site
((HKY.clock.filtered - HKY.Force.clock.filtered)[2,] /  HKY.clock.filtered[1, ])
```

MG94 nonclock case
```{r}
improvement.lmt <- 0.16
plot(colSums(MG94.nonclock.filtered[9:20, ]), MG94.nonclock.filtered[8, ],
     type = "n", xlab = "Total branch length", ylab = "Tau" )
col.color <- rep("black", dim(MG94.nonclock.filtered)[2])
col.color[((MG94.nonclock.filtered - MG94.Force.nonclock.filtered)[2,] / MG94.nonclock.filtered[1]) < improvement.lmt] <- "red"
points(x = colSums(MG94.nonclock.filtered[9:20, ]), y = MG94.nonclock.filtered[8, ],
       type = "p", col = col.color, bg = col.color)
legend("topright", 
       c(paste("lnL improvement per site > ", toString(improvement.lmt), sep = ""),
         paste("lnL improvement per site < ", toString(improvement.lmt), sep = "")),
       lty = c(1, 1), 
       lwd = c(2.5, 2.5),
       col = c("black", "red"))
title("MG94 nonclock")

# lnL improvement per site
((MG94.nonclock.filtered - MG94.Force.nonclock.filtered)[2,] / MG94.nonclock.filtered[1])
```

MG94 clock case
```{r}
improvement.lmt <- 0.4
plot(colSums(MG94.clock.filtered[9:20, ]), MG94.clock.filtered[8, ],
     type = "n", xlab = "Total branch length", ylab = "Tau" )
col.color <- rep("black", dim(MG94.clock.filtered)[2])
col.color[((MG94.clock.filtered - MG94.Force.clock.filtered)[2,] / MG94.clock.filtered[1]) < improvement.lmt] <- "red"
points(x = colSums(MG94.clock.filtered[9:20, ]), y = MG94.clock.filtered[8, ],
       type = "p", col = col.color, bg = col.color)
legend("topright", 
       c(paste("lnL improvement per site > ", toString(improvement.lmt), sep = ""),
         paste("lnL improvement per site < ", toString(improvement.lmt), sep = "")),
       lty = c(1, 1), 
       lwd = c(2.5, 2.5),
       col = c("black", "red"))
title("MG94 clock")

# lnL improvement per site
((MG94.clock.filtered - MG94.Force.clock.filtered)[2,] / MG94.clock.filtered[1])
```
